A Framework for Equivalence of Cast Calculi and a new Cast Representation

### 2020-10-14 paper.tex
Refine appendix
remove the last subsection in related work because the subsection is too short and not very informative.

In this section we review publications that contribute dynamic semantics
applicable to a variety of cast representations
(Subsection~\ref{subsec:parameterized-dynamics}),
proofs of correctness of cast representations
(Subsection~\ref{subsec:related-work-other-proofs}),
and relationship between hypercoercions and other cast representations
(Subsection~\ref{subsec:related-work-other-cast-reprs}).

@@

\subsection{Other Cast Representations}
\label{subsec:related-work-other-cast-reprs}

Hypercoercions is inspired by coercions in normal form and supercoercions
and ends up having a symmetrical definition similar to threesomes.

@@

Lemma~\ref{lem:weak-bisimulation} is proved by case analysis on \bisims{s_1}{s_1'}{T}.
Function call is the most interesting case. In this case the function value in
\CMachine{B}
must be of the form 
\[
v_1 = \vfuncc{
		\vfuncc{
			\vfunc{x}{S_1}{e}{E}
		}{S_1}{T_1}{l_1}{S_2}{T_2}
		\ldots
	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
\]
By induction of the sequence of casts, we know \scont{v_2}{\Kcons{\FappOX{v_1}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2}{\applyCast{v_2}{\ccast{S_n}{\bar{l}}{S_{n-1}}}}{} \\
\ldots \\
\mlet{v_2}{\applyCast{v_2}{\ccast{S_2}{\bar{l}}{S_1}}}{} \\
\sexpr{e}{E[x:=v_2]}{
	\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{
	    \ldots
	    \Kcons{\Fcast{\ccast{T_{n-1}}{l}{T_n}}}{K}}
}
\end{array}
\]
% Assuming \bisimv{v_1}{v_1'}{\Pfunc{S_n}{T_n}} and \bisimv{v_2}{v_2'}{S_n}.
As for \SMachine{C}, the function value must be of the form
\[
v_1' = \ecast{\vfunc{x}{S}{e}{E'}}{\Pfunc{c}{d}}
\]
where
\[
\begin{array}{l}
\bisimc{(\ccast{S_n}{\bar{l}}{S_{n-1}} \ldots \ccast{S_2}{\bar{l}}{S_1})}{c}{S_n}{S_1} \\
\bisimc{(\ccast{T_1}{l}{T_1} \ldots \ccast{T_{n-1}}{l}{T_n})}{d}{T_1}{T_n} \\
\end{array}
\]
By the definition of \applyContName\ we know \applyCont{v_2'}{\Kcons{\FappOX{v_1'}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2'}{\denote{c}(v_2')}{} \\
\sexpr{e}{E'[x:=v_2']}{\extCont{d}{K'}}
\end{array}
\]
Intuitively, we need to show the sequence of let bindings in \CMachine{B}
bisimulate the single let binding in \SMachine{C}, and that the two 
extended continuations bisimulate each other. The first part follows from

>>>>

In this section we review publications that contribute dynamic semantics
applicable to a variety of cast representations
(Subsection~\ref{subsec:parameterized-dynamics}),
and proofs of correctness for cast representations
(Subsection~\ref{subsec:related-work-other-proofs}).
% and relationship between hypercoercions and other cast representations
% (Subsection~\ref{subsec:related-work-other-cast-reprs}).

@@

% \subsection{Other Cast Representations}
% \label{subsec:related-work-other-cast-reprs}

% Hypercoercions is inspired by coercions in normal form and supercoercions
% and ends up having a symmetrical definition similar to threesomes.

@@

Lemma~\ref{lem:weak-bisimulation} is proved by case analysis on \bisims{s_1}{s_1'}{T}.
Function call is the most interesting case. In this case the function value in
\CMachine{B}
must be of the form 
\[
v_1 = \vfuncc{
		\vfuncc{
			\vfunc{x}{S_1}{e}{E}
		}{S_1}{T_1}{l_1}{S_2}{T_2}
		\ldots
	}{S_{n-1}}{T_{n-1}}{l_{n-1}}{S_n}{T_n}
\]
By induction of the sequence of casts, we know \scont{v_2}{\Kcons{\FappOX{v_1}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2}{\applyCast{v_2}{\ccast{S_n}{\bar{l}}{S_{n-1}}}}{} \\
\ldots \\
\mlet{v_2}{\applyCast{v_2}{\ccast{S_2}{\bar{l}}{S_1}}}{} \\
\sexpr{e}{E[x:=v_2]}{
	\Kcons{\Fcast{\ccast{T_1}{l}{T_2}}}{
	    \ldots
	    \Kcons{\Fcast{\ccast{T_{n-1}}{l}{T_n}}}{K}}
}
\end{array}
\]
% Assuming \bisimv{v_1}{v_1'}{\Pfunc{S_n}{T_n}} and \bisimv{v_2}{v_2'}{S_n}.
As for \SMachine{C}, the function value must be of the form
\[
v_1' = \ecast{\vfunc{x}{S}{e}{E'}}{\Pfunc{c}{d}}
\]
where
\[
\begin{array}{l}
\bisimc{(\ccast{S_n}{\bar{l}}{S_{n-1}} \ldots \ccast{S_2}{\bar{l}}{S_1})}{c}{S_n}{S_1} \\
\bisimc{(\ccast{T_1}{l}{T_1} \ldots \ccast{T_{n-1}}{l}{T_n})}{d}{T_1}{T_n} \\
\end{array}
\]
By the definition of \applyContName\ we know \applyCont{v_2'}{\Kcons{\FappOX{v_1'}}{K}} will
transition to
\[
\begin{array}{l}
\mlet{v_2'}{\denote{c}(v_2')}{} \\
\sexpr{e}{E'[x:=v_2']}{\extCont{d}{K'}}
\end{array}
\]
Intuitively, we need to show the sequence of let bindings in \CMachine{B}
bisimulate the single let binding in \SMachine{C}, and that the two 
extended continuations bisimulate each other. The first part follows from 
the properties of Cast ADT (Definition~\ref{def:cast-rep}) and the premise that 
cast applications preserve the bisimulation relation. The second part
is straightforward to prove.
